Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
minor fix for lazyD cast calc

In the reduction relation $ \judgeDCreduce{s}{s} $, to evaluate a cast 
expression, the machine move the 
cast to the continuation and evaluate the inner expression. To apply a casted 
function, the machine firstly cast $ v_1 $, the operand, then apply the casted 
operand to $ v_2 $, the un-casted function, and finally cast the result of the 
function application. To take out the first (resp. second) part of a casted 
pair, the machine firstly take out the first (resp. second) part of $ v $, the 
un-casted pair, and cast the result. To case-split a sum, the machine looks 
deep inside the value to find out whether it is a left injection or a right 
one.
\todo[inline]{Change the rules for case to be small step, i.e.,
	the case function should not be recursive. -Jeremy}
Along the way, the machine accumulate the pending casts onto the 
continuations. To cast a value, the machine try to apply the cast to the value. 
If the cast succeeds, the machine returns the result to the next continuation. 
If the cast fails, the machine halts with the blame label.

@@

\subsection{The \lazyD{} cast calculus}

@@

	\end{array}
	\]
	\caption{Definition of $ applyCast $ for \lazyD}
\end{figure}

We conjecture that this CEK machines agree with the \lazyD{} cast calculus in 
\citet{siek2012interpretations}.
We will show in \hyperref{sec:hypercoercion} that this abstract machine is 
equivalent to an abstract machine that represents casts with hypercoercions.

>>>>

The reduction relation $ \judgeDCreduce{s}{s} $ depends on $ applyCast $, a 
function depending on blame strategies. We will give the definitions of $ 
applyCast $ shortly.
To evaluate a cast 
expression, the machine move the 
cast to the continuation and evaluate the inner expression. To apply a casted 
function, the machine firstly cast $ v_1 $, the operand, then apply the casted 
operand to $ v_2 $, the un-casted function, and finally cast the result of the 
function application. To take out the first (resp. second) part of a casted 
pair, the machine firstly take out the first (resp. second) part of $ v $, the 
un-casted pair, and cast the result. To case-split a sum, the machine looks 
deep inside the value to find out whether it is a left injection or a right 
one.
\todo[inline]{Change the rules for case to be small step, i.e.,
	the case function should not be recursive. -Jeremy}
Along the way, the machine accumulates the pending casts onto the 
continuations. To cast a value, the machine try to apply the cast to the value. 
If the cast succeeds, the machine returns the result to the next continuation. 
If the cast fails, the machine halts with the blame label.

@@

\subsection{The \lazyD{} cast calculus}
\todo[inline]{I want to merge this and the following subsetion to the 
subsection above. -KC}

@@

	\end{array}
	\]
	\caption{Definition of $ applyCast $ for \lazyD}
	\label{fig:applyCast-D-C}
\end{figure}

\figref{fig:applyCast-D-C} defines the $ applyCast $ for \lazyD. 
We conjecture that with this $ applyCast $, the CEK machine in 
\figref{machine-cekc} would agree with the \lazyD{} cast calculus in 
\citet{siek2009exploring}.
